The imputation methods big test

### 2020-04-30 pd2.Rmd
poprawiona legenda

```{r dataset description, message = FALSE, warning=FALSE, cache = TRUE}
### TU KOD HANI BEDZIE DO WKLEJENIA

@@

Here are the results:

@@

require(scales)
ggplot(data=imptimes, aes(x = dataset_id, y = value, color = variable, shape = variable)) +
  geom_point() + 
  ggtitle("Datasets' imputations times") +
  theme_gray() +
  scale_y_continuous(trans = log2_trans(),
    breaks = trans_breaks("log2", function(x) 2^x),
    labels = trans_format("log2", math_format(2^.x))) +
  labs(x = "Dataset Id",
       y = "Imputation time [in seconds]",
       color = "Legend") +
  scale_color_manual(name = "imputation name", values = colors) +
  theme(legend.position="right",
        plot.title = element_text(hjust = 0.5))
```

>>>>

```{r dataset description, message = FALSE, warning=FALSE, cache = TRUE}

@@

Here are the results. NA indicates that method returned error:

@@

require(scales)
ggplot(data=imptimes, aes(x = dataset_id, y = value, color = variable, shape = variable)) +
  geom_point() + 
  ggtitle("Datasets' imputations times") +
  theme_gray() +
  scale_y_continuous(trans = log2_trans(),
    breaks = trans_breaks("log2", function(x) 2^x),
    labels = trans_format("log2", math_format(2^.x))) +
  labs(x = "Dataset Id",
       y = "Imputation time [in seconds]",
       color = "Legend") +
  scale_color_manual(name = "imputation name", values = colors) +
  theme(legend.position="right",
        plot.title = element_text(hjust = 0.5)) +
  #scale_colour_manual(name = "Treatment & State",
  #                    labels = c("Control, Non-F", "Control, Flwr", "Exclosure, Non-F", "Exclosure, Flwr"),
  #                    values = c("blue", "red", "blue", "red")) +   
  scale_shape_manual(name = "imputation name",
                     values = 15:19L)
